Sequential rank agreement methods for comparison of lists

### 2015-08-11 latex/paper.Rnw
Submitted version

The sequential rank agreement plotted in Figure~\ref{fig:example1}
shows how many ranks apart we on average expect the genes found in the
top $d$ part of the lists to be for each depth $d$.  It can be seen
that the sequential rank agreement limits are better towards the top
of the lists (smaller values on the $y$ axis) corresponding to
\emph{better} agreement than in the tails of the lists.

@@

\section{Application}
We now consider an application of the sequential rank agreement to two
data sets consisting of MALDI-TOF (Matrix-Assisted Laser
Desorption/Ionization Time Of Flight) mass spectra obtained from blood
samples from patients with either benign or malignant ovarian
tumors. The data sets are sub-samples of the Danish MALOVA and DACOVA
study populations.

@@

\textbf{Our applications show that XXX
Through simulations we showed that XXX --- afventer Andreas.}

@@

Finally, we have --- whenever possible --- used all available ranks
from the lists.  We could choose to censor the rankings of all the
items that were deemed not to be significant if information on both
rankings and the corresponding evidence for significance was
available. That would ensure that there would be put less emphasis on
the agreement of the non-significant items and it would be easier to
identify a change in agreement among the items that were deemed to
relevant. In our application section we have successfully introduced
such an artificial censoring for the predictor rankings obtained with
ridge regression.

@@

Another caveat with the way the sequential rank agreement is defined
is the use of the standard deviation to measure agreement. The
standard deviation is an integral part of the limits-of-agreement as
discussed by \citet{alt:bland:1983}. However, the standard deviation
can also be unstable when the number of observations is low and
alternative measures such as the mean absolute deviance may prove more
stable in some situations. However, the current definition using the
standard deviation is analogous to the approach used for agreement in
method comparison studies.

>>>>

The sequential rank agreement plotted in Figure~\ref{fig:example1}
shows how many ranks apart we on average expect the genes found in the
top $d$ part of the lists to be for each depth $d$.  It can be seen
that the sequential rank agreement limits are better towards the top
of the lists (smaller values on the $y$ axis) corresponding to
\emph{better} agreement than in the tails of the lists. It is clear
from the curve in Figure~\ref{fig:example1} that there is a
substantial drop in agreement even after the first depth. Thus, if we
were to restrict attention to a small set of predictors then we would
focus on predictors 2124, 829, and 378 as seen in Table~\ref{tab1}.

@@

\section{Application to ovarian cancer data}
We now consider an application of the sequential rank agreement to two
data sets consisting of MALDI-TOF (Matrix-Assisted Laser
Desorption/Ionization Time Of Flight) mass spectra obtained from blood
samples from patients with either benign or malignant ovarian
tumors. The data sets are sub-samples of the Danish MALOVA and DACOVA
study populations.

@@

@@

Finally, we have --- whenever possible --- used all available ranks
from the lists.  We could choose to censor the rankings of all the
items that were deemed not to be significant if information on both
rankings and the corresponding evidence for significance was
available. That would ensure that there would be put less emphasis on
the agreement of the non-significant items and it would be easier to
identify a change in agreement among the items that were deemed to
be relevant. In our application section we have successfully introduced
such an artificial censoring for the predictor rankings obtained with
ridge regression.

@@

Another caveat with the way the sequential rank agreement is defined
is the use of the standard deviation to measure agreement. The
standard deviation is an integral part of the limits-of-agreement as
discussed by \citet{alt:bland:1983}. However, the standard deviation
can also be unstable when the number of observations is low and
alternative measures such as the median absolute deviance may prove more
stable in some situations. However, the current definition using the
standard deviation is analogous to the approach used for agreement in
method comparison studies so we have used that.
